Mallows, Black-box combinatorial optimization, limited budget, ???

### 2020-10-21 paper/main.tex
update paper

 \caption{Mean fitness (and standard deviation) of the best solution found at the end of each run, over 10 independent runs for each problem instance. The 95\% confidence interval corresponds to the two independent samples t-test on the mean of the difference between the fitness of UMM minus the one of CEGO. Mean runtime is measured in seconds. If a run of  CEGO was not able to reach 400 function evaluations (FEs) in 3 days, it was terminated earlier. This was the case for all LOP instances shown.\label{tab:results}}

>>>>

 \caption{Mean fitness (and standard deviation) of the best solution found at the end of each run, over 10 independent runs for each problem instance. The 95\% confidence interval corresponds to the two independent samples t-test on the mean of the difference between the fitness of UMM minus the one of CEGO. Mean runtime is measured in hours. If a run went over 72 hours, of  CEGO was not able to reach 400 function evaluations (FEs) in 72 hours, it was terminated earlier. This was the case for all LOP instances shown.\label{tab:results}}
